---
output: github_document
---

# Learning Shiny

I am on an adventure to learn to code Shiny apps (applications based in R functionality and syntax) to be used as stats learning aids!

# Upcomming

* Continuous distribution app using dynamic distribution charactaristics
* `q*()`, `p*()`, `d*()` demonstration
* CLT demonstration

# Progress

## An extension with increased complexity: Basic Discrete Distribution Demo

> **short name**: basicdisretedemo  
> **URL**: [ganovak.shinyapps.io/basicdiscretedemo](https://ganovak.shinyapps.io/basicdiscretedemo/)   
> **Objective**: Visually demonstrate effect of parameters on support and PMF of commonly used
discrete distributions  
> **Input**:    
>   Discrete Uniform:  
>       A, B: integer in [0, 100] NOTE: bounds are arbitrary  
>   Binomial:  
>       n: integer in [0,100] NOTE: upper bound is arbitrary  
>       p: real in [0,1]  
>   Poisson:  
>       λ: real in (0, ∞)    
> **Output**: 
>   Bar plot of PMF of specified distribution with user specified parameters  

### New features

* Tabbed Layout
* Use of Unicode characters
* Addition of discrete uniform and Poisson distributions
* Addition of text elements

```{r, echo = FALSE}
knitr::include_app("https://ganovak.shinyapps.io/basicdiscretedemo/")
```

## My first app: Binomial Distribution Demo

> **short name**: binomdemo  
> **URL**: [ganovak.shinyapps.io/binomdemo](https://ganovak.shinyapps.io/binomdemo/)  
> **Function**: Visually demonstrate effect of parameters in binomial distribution  
> **Input**:  
>   n: integer in [0,100] NOTE: upper bound is arbitrary  
>   p: real in [0,1]  
> **Output**: Bar plot of PMF of binomial distribution with user specified parameters  

```{r, echo = FALSE, out.width = 1000}
knitr::include_app("https://ganovak.shinyapps.io/binomdemo/",
                   height = "4000px")
```

